Music Recommendation System Using the Million Song Dataset

### 2015-05-08 writeup/MSDgroupwriteup.tex
Update MSDgroupwriteup.tex

One explanation for the very low MAP scores using PMF was that the number of plays that were used are different from the typical bounded ratings PMF is typically used on. Using implicit user feedback (number of plays) instead of explicit user feedback (ratings) has been shown in literature, such as \citet{hu2008collaborative}, to create various issues. One of the main issues is that implicit feedback is inherently noisy and does not measure negative feedback. Listeners may have played a song and simply found out that they disliked the song. The other main issue is that the exact number of plays could have a significantly different meaning across different users. For example, an avid listener who has played a song five times could have a different meaning as compared to a listener that has played songs at most five times.

>>>>

One explanation for the very low MAP scores using PMF was that the number of plays that were used were different from the typical bounded ratings PMF is typically used on. Using implicit user feedback (number of plays) instead of explicit user feedback (ratings) has been shown in literature, such as \citet{hu2008collaborative}, to create various issues. One of the main issues is that implicit feedback is inherently noisy and does not measure negative feedback. Listeners may have played a song and simply found out that they disliked the song. The other main issue is that the exact number of plays could have a significantly different meaning across different users. For example, an avid listener who has played a song five times could have a different meaning as compared to a listener that has played songs at most five times.
